Imputation of incomplete multilevel data

### 2024-10-18 manuscript.qmd
add results tables

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
# print everything as kable ----
knit_print.data.frame <- function (x, options, ...) {
  knitr::kable(x) |> knitr::knit_print(options, ...)
}
registerS3method("knit_print", "data.frame", knit_print.data.frame)
options(scipen = 999, digits = 3)
```

@@

- it accounts for missing data uncertainty
- it accounts for parameter uncertainty
- can yield valid inference without additional adjustments

@@

![](https://stefvanbuuren.name/fimd/fig/ch01-miflow-1.png){width=80%}
:::

@@

Setup `R` environment
```{r, message=FALSE, warning=FALSE}
library(mice)         # for imputation
library(miceadds)     # for imputation
library(micemd)       # for imputation
library(ggmice)       # for visualization
library(ggplot2)      # for visualization
library(dplyr)        # for data wrangling
library(lme4)         # for multilevel modeling
library(broom)        # for tidying model output
library(broom.mixed)  # for tidying model output
```

@@

@@

<!-- 1.	Inspect incomplete data -->
<!-- a.	Explore variables: determine imputation methods with str() and ggmice(),  -->
<!-- b.	If necessary, add variables for polynomial terms -->
<!-- c.	Explore missingness: evaluate missing data patterns with plot_pattern() -->
<!-- d.	Determine imputation model predictors using plot_corr(), plot_flux(), and ggmice() -->
<!-- 2.	Build imputation models -->
<!-- a.	Create methods vector with imputation methods using make.methods() -->
<!-- b.	Create predictor matrix with imputation model predictors using make.predictorMatrix() -->
<!-- c.	Evaluate imputation models using plot_pred() -->
<!-- 3.	Run imputation algorithm -->
<!-- a.	Impute: fill in the missing values with mice() -->
<!-- b.	Inspect convergence: visualize algorithmic convergence with plot_trace() -->
<!-- c.	If necessary, add iterations -->
<!-- 4.	Evaluate imputations -->
<!-- a.	Inspect imputed values: assess imputed values with ggmice(), PPC? -->
<!-- b.	Analyze imputed data: fit the model of scientific interest with lmer()   -->
<!-- c.	Evaluate missingness metrics with testEstimates() -->
<!-- d.	If necessary, add imputations -->
<!-- 5.	Interpret results and report -->

@@

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
# print everything as kable ----
knit_print.data.frame <- function(x, options, ...) {
  knitr::kable(x) |> knitr::knit_print(options, ...)
}
registerS3method("knit_print", "data.frame", knit_print.data.frame)
options(scipen = 999, digits = 3)
```

@@

- it accounts for missing data uncertainty
- it accounts for parameter uncertainty
- can yield valid inference without additional adjustments 
:::

@@

![](https://stefvanbuuren.name/fimd/fig/ch01-miflow-1.png){width=80%}

@@

Setup `R` environment
```{r, message=FALSE, warning=FALSE}
library(mice)         # for imputation
library(miceadds)     # for imputation
library(micemd)       # for imputation
library(ggmice)       # for visualization
library(ggplot2)      # for visualization
library(dplyr)        # for data wrangling
library(lme4)         # for multilevel modeling
library(broom)        # for tidying model output
library(broom.mixed)  # for tidying model output
library(sjPlot)       # for results tables
```

@@

```{r}
tab_model(mod_true_intercept, mod_true_predictors, mod_true_randomslope, mod_true_interaction)
```

@@

```{r}
tab_model(mod_cca_intercept, mod_cca_predictors, mod_cca_randomslope, mod_cca_interaction)
```
<!-- 1.	Inspect incomplete data -->
<!-- a.	Explore variables: determine imputation methods with str() and ggmice(),  -->
<!-- b.	If necessary, add variables for polynomial terms -->
<!-- c.	Explore missingness: evaluate missing data patterns with plot_pattern() -->
<!-- d.	Determine imputation model predictors using plot_corr(), plot_flux(), and ggmice() -->
<!-- 2.	Build imputation models -->
<!-- a.	Create methods vector with imputation methods using make.methods() -->
<!-- b.	Create predictor matrix with imputation model predictors using make.predictorMatrix() -->
<!-- c.	Evaluate imputation models using plot_pred() -->
<!-- 3.	Run imputation algorithm -->
<!-- a.	Impute: fill in the missing values with mice() -->
<!-- b.	Inspect convergence: visualize algorithmic convergence with plot_trace() -->
<!-- c.	If necessary, add iterations -->
<!-- 4.	Evaluate imputations -->
<!-- a.	Inspect imputed values: assess imputed values with ggmice(), PPC? -->
<!-- b.	Analyze imputed data: fit the model of scientific interest with lmer()   -->
<!-- c.	Evaluate missingness metrics with testEstimates() -->
<!-- d.	If necessary, add imputations -->
<!-- 5.	Interpret results and report -->

@@

```{r}
# tab_model(mod_imp_intercept, mod_imp_predictors, mod_imp_randomslope, mod_imp_interaction)
```
